---
title: "hw_week3"
author: "Peng Yi Ting"
date: "2018年10月3日"
output: html_document
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install and libary ggplot

```{r}
library(ggplot2)

```

## Using inner data: women and change the form of the data

Using inner data and giving a summary statistics. 
```{r}
##using inner data and change the form of the data

d1<-women
d1
##note：using captial words on the first letter of "v"iew
View(d1)
summary(d1)
```

## Plot a photogram

First, it doesn't have dot on the photogram.
```{r}
ggplot(d1, aes(x=height, y=weight))
```

Add dots into the photogram.
```{r}
ggplot(d1, aes(x=height, y=weight))+
  geom_point()
```

Change the pattern of dots.
```{r}
ggplot(d1, aes(x=height, y=weight)) +
  geom_point(color = "red", shape = 8)
```

Add details of labels.
```{r}
ggplot(d1, aes(x=height, y=weight)) +
  geom_point(color = "red", shape = 8)+
  labs(subtitle="The relationship between height and weight",
       y="Weight(lb)",
       x="Height(ft)",
       title="Scatterplot",
       caption="Source: women")

```
---
##Part2:Convert unit into cm and kg.
```{r}
d2<-d1
d2<-data.frame(d2$height*2.54,d2$weight*0.45)
View(d1)
View(d2)
names(d2)<-c("height", "weight")
d2
```

Plot a photogram
```{r}
ggplot(d2, aes(x=height, y=weight))
```

Add dots into the photogram.
```{r}
ggplot(d2, aes(x=height, y=weight))+
  geom_point()
```

Change the pattern of dots.
```{r}
ggplot(d2, aes(x=height, y=weight)) +
  geom_point(color = "blue", shape = 9)
```

Add details of labels.
```{r}
ggplot(d2, aes(x=height, y=weight)) +
  geom_point(color = "blue", shape = 9)+
  labs(subtitle="The relationship between height and weight",
       y="Weight(kg)",
       x="Height(cm)",
       title="Scatterplot2",
       caption="Source: women")

```


